\begin{acknowledgements}
	First and foremost, I would like to thank my supervisor and teacher,
	Professor Jiang Bin, for the valuable lessons about Intelligent Optimization
	Algorithms and the mentoring from afar during my research work. These
	lessons, combined with the sessions where students needed to present a
	thesis and debate about it, were eye-opening and provided excellent
	preparation for our research work.

	Because of Covid-19, I deeply regret my inability to return to China to
	continue adequately with my studies. Being 9000km away from the laboratory
	and its incredible students, my supervisor and all the helping resources and
	hardware may have interfered slightly with my research. Still, regardless of
	the many obstacles, I wholeheartedly gave my best to deliver a work I can be
	proud of.

	Secondly, I would thank my friend MELNYK Pavlo, a Ph.D. student, for his
	guidance throughout the research process, who helped me shape the overall
	structure of this thesis and provided needed encouragement alongside the
	occasional pep talks!

	During these two years of researching and writing my thesis, I also had the
	opportunity to work as a Software Engineer at a few start-ups, working with
	Python and PyTorch, utilizing the knowledge I leveraged during my research and
	experiments. These experiences working alongside the studies and research work
	done at Hunan University definitely confirmed my intention to pursue this field
	of work.

	I would also like to thank Hunan University for allowing me first to study
	Mandarin and then for my Master in Computer Science. Finally, I am grateful
	to China Scholarship Council (CSC) for awarding me a scholarship that
	allowed me to study in China.

	Regardless of being unable to return to China, this country has held a deer
	spot in my heart, and it has since the very first moment I arrived in China.
	Its welcoming and giving people, mouthwatering food, and beautiful
	sceneries, I cannot wait to be able to return, to give back some of what I
	received.
\end{acknowledgements}
